\thesistitle{Example Game Programming Thesis. With a long title to test the wrapping of the box}
\thesisauthor{Simon McCallum}
\thesisauthorA{Ivar Farup}
%\thesisauthorB{}
%\thesisauthorC{}
\thesissupervisor{Rune Hjelsvold}
%\thesissupervisorA{} %second supervisor

\gmtkeywords{Thesis, Latex, Template, IMT}
\gmtdesc{This is the short description of a bachelor thesis}
\gmtnumber{-} % this is the number given to your project. May not be used  

\gmtoppdragsgiver{\NTNU}
\gmtcontact{Erik Helm\aa s, erik.helmas@hig.no, 61135000}




\thesisdate{25.05.2016}
\thesisyear{2016}

\gmtappnumber{} %numebr of appendixes
\gmtpagecount{} %currently auto calculated but might be wrong

\thesistitle{English title.}
\gmtkeywords{English, Thesis}
\gmtdesc{This should be in English, I thought I would add some more text
to make sure that it ran over multiple lines. I will need to check the page
number feild as it probably should be just the core pages without the
appendices.  Currently it returns the last page of the whole document. 
If I cannot work it out, I will provide two inputs, nmtnumberpages and nmtappnumber.
That should do the job.}



\thesistitleNOR{Norwegian title.}
\gmtkeywordsNOR{Norway, Norsk}
\gmtdescNOR{This should be in Norwegian, I thought I would add some more text
to make sure that it ran over multiple lines. I will need to check the page
number feild as it probably should be just the core pages without the
appendices.  Currently it returns the last page of the whole document. 
If I cannot work it out, I will provide two inputs, gmtnumberpages and gmtappnumber.
That should do the job.}
